---
title: "Tidying Touch Interaction Data - Working Research Question: Predict PQ from Touch Data?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs-TidyingTouchData/',
                      echo=FALSE, warning=FALSE, message=FALSE)
library(lattice)
library(Amelia)
library(pander)
library(ggplot2)
library(e1071)
library(readr)
library(GGally)

setwd("~/Auswertungen/2016-11_Studie_01/Auswertung/FeatureEngineering")

univariateViewOn <- function(variable, threshold){
  pander(paste0(variable, ": \n"))

  pander(paste0("Cut at ", threshold))
  
  sample <- sample(which(data.experiment.selectedVariables[[variable]] < threshold), 3000)
  
  ggplot(data = data.experiment.selectedVariables[data.experiment.selectedVariables[[variable]] < threshold,], aes(User, get(variable), fill=User)) + geom_boxplot(alpha=0.3, outlier.size = 0.5, outlier.alpha = 1) + geom_jitter(data = data.experiment.selectedVariables[sample,], aes(User, get(variable)), alpha=0.75, size=0.5, shape=0, color="blue") + labs(title = variable)
  
  data.experiment.selectedVariables <- data.experiment.selectedVariables[data.experiment.selectedVariables[[variable]] < threshold,]

  pander("Statistics on time_between_touches: \n")
  summary <- summary(data.experiment.selectedVariables[[variable]])

  summary <- data.frame(table(summary), names(summary))
  summary$Freq <- NULL
  colnames <- summary$names.summary.
  summary <- t(summary)
  colnames(summary) <- colnames
  summary <- summary[-2,]
  summary$sd <- sd(data.experiment.selectedVariables[[variable]], na.rm = TRUE)
  summary$kurtosis <- kurtosis(data.experiment.selectedVariables[[variable]], na.rm = TRUE)
  summary$skew <- skewness(data.experiment.selectedVariables[[variable]], na.rm = TRUE)

  pander(data.frame(summary))
}

# ToDo: not only these, but more VPs...
VP.numbers <- 3:33
User.ids <- 100:130
```

# Data from PflegeTab-Database

To get the data from the database, run the skript in [getDataFromDB.R](../getDataFromDB.R).
You'll need to connect to the correct server (the skript uses do6.pflegetab.de) via terminal.

Set the working directory.

Set an appropriate destination folder for your data to be saved in, e.g., the folder your analysis will take place in.

# Distribution of (Touch Down) Events in current experiment

```{r data from pflegetab database, fig.show='hold', out.width="50%"}

if ( !file.exists("01_DataExperiment_unprocessed.Rda") ) {
  
  load("RawData.Rda")
  
  rm(tracking.apps.raw, tracking.loginLogout.raw, tracking.menu.raw, tracking.notifications.raw, tracking.reward.raw, tracking.screen.raw)
  
  # 
  tracking.touches.experiment <- tracking.touches.raw[tracking.touches.raw$user_id %in% User.ids,]
  tracking.appStartClose.experiment <- tracking.appStartClose.raw[tracking.appStartClose.raw$user_id %in% User.ids,]
  tracking.quiz.experiment <- tracking.quiz.raw[tracking.quiz.raw$user_id %in% User.ids,]
  tracking.spell.experiment <- tracking.spell.raw[tracking.spell.raw$user_id %in% User.ids,]
  
  tracking.touches.experiment$originTable <- "touches"
  tracking.appStartClose.experiment$originTable <- "appStartClose"
  tracking.quiz.experiment$originTable <- "quiz"
  tracking.spell.experiment$originTable <- "spell"
  
  tracking.touches.experiment$eventCode <- tracking.touches.experiment$event
  tracking.appStartClose.experiment$eventCode <- tracking.appStartClose.experiment$event
  tracking.quiz.experiment$eventCode <- tracking.quiz.experiment$event
  tracking.spell.experiment$eventCode <- tracking.spell.experiment$event
  
  tracking.touches.experiment$event <- factor(tracking.touches.experiment$event, labels = c("touch.down", "touch.release"))
  tracking.appStartClose.experiment$event <- factor(tracking.appStartClose.experiment$event, labels = c("app.started", "app.closed"))
  tracking.quiz.experiment$event <- factor(tracking.quiz.experiment$event, labels = c("loaded", "wrong.button", "correct.button"))
  tracking.spell.experiment$event <- factor(tracking.spell.experiment$event, labels = c("loaded", "wrong.button", "correct.button", "wrong.placed", "correctly.placed", "completed.word"))
  
  data.experiment.unsorted <- merge(tracking.touches.experiment, tracking.appStartClose.experiment, suffixes = c(".touches", ".appStartClose"), all = TRUE)
  data.experiment.unsorted <- merge(data.experiment.unsorted, tracking.quiz.experiment, all = TRUE)
  data.experiment.unsorted <- merge(data.experiment.unsorted, tracking.spell.experiment, all = TRUE)
  data.experiment <- data.frame(data.experiment.unsorted[order(data.experiment.unsorted$timestamp),])
  rownames(data.experiment)  <- NULL
  
  save(data.experiment, VP.numbers, User.ids, file = "01_DataExperiment_unprocessed.Rda")
  rm(list = ls())
}

if ( !file.exists("02_DataExperiment_labeledWithConds+SessionNrs.Rda") ) {

  load("01_DataExperiment_unprocessed.Rda")
  
  ## get rid of the NAs in the spell-data for freezing or tinyIcons
  # while(any(is.na(data.experiment$freezing[data.experiment$originTable == "spell"]))){
  for(i in 1:5){
    data.experiment$freezing[data.experiment$originTable == "spell"] <- ifelse(!is.na(data.experiment$freezing[which(data.experiment$originTable == "spell")+1]),  data.experiment$freezing[which(data.experiment$originTable == "spell")+1], data.experiment$freezing[which(data.experiment$originTable == "spell")-1])
    data.experiment$tinyIcons[data.experiment$originTable == "spell"] <- ifelse(!is.na(data.experiment$tinyIcons[which(data.experiment$originTable == "spell")+1]),  data.experiment$tinyIcons[which(data.experiment$originTable == "spell")+1], data.experiment$tinyIcons[which(data.experiment$originTable == "spell")-1])
    data.experiment$lowContrast[data.experiment$originTable == "spell"] <- ifelse(!is.na(data.experiment$lowContrast[which(data.experiment$originTable == "spell")+1]),  data.experiment$lowContrast[which(data.experiment$originTable == "spell")+1], data.experiment$lowContrast[which(data.experiment$originTable == "spell")-1])
    data.experiment$noFeedback[data.experiment$originTable == "spell"] <- ifelse(!is.na(data.experiment$noFeedback[which(data.experiment$originTable == "spell")+1]),  data.experiment$noFeedback[which(data.experiment$originTable == "spell")+1], data.experiment$noFeedback[which(data.experiment$originTable == "spell")-1])
  }
  
  data.experiment$appCode <- data.experiment$app
  data.experiment$App <- factor(data.experiment$appCode, labels = c("Quiz", "Spell"))
  data.experiment$User <- as.factor(data.experiment$user_id)
  
  # ToDo: Code additional Conditions, e.g. Adaption
  data.experiment$condCode <- 0
  data.experiment$condCode[data.experiment$freezing == 1 & data.experiment$tinyIcons == 0] <- 1
  data.experiment$condCode[data.experiment$freezing == 0 & data.experiment$tinyIcons == 0] <- 2
  data.experiment$condCode[data.experiment$freezing == 0 & data.experiment$tinyIcons == 1] <- 3
  data.experiment$Cond <- factor(data.experiment$condCode, labels = c("noInfo", "Freezing", "Normal", "TinyIcons"))
  
  appStart.indices <- which(data.experiment$event == "app.started")
  sessionNr <- 0
  startCounter <- 1
  for(i in 1:dim(data.experiment)[1]){
    data.experiment$sessionNr[i] <- sessionNr
    if(i == appStart.indices[startCounter] & startCounter <= length(appStart.indices)){
      startCounter <- startCounter + 1
      sessionNr <- sessionNr + 1
    }
  }
  
  
  data.experiment <- data.experiment[data.experiment$Cond != "noInfo" &  data.experiment$event != "app.started" &  data.experiment$event != "app.closed",]
  data.experiment$Cond <- factor(data.experiment$Cond)
  
  # ToDo: Find appropriate handling for different experiments!
  table(data.experiment$sessionNr)
  sessionMembers <- as.data.frame(table(data.experiment$sessionNr))
  sessionMembers[sessionMembers$Freq < 5,] # 4 sessions that are not rated, started and immediately stopped app -> leaves 372 sessions ;)
  
  data.experiment <- data.experiment[!(data.experiment$sessionNr %in% sessionMembers$Var1[sessionMembers$Freq < 5]),]
  rownames(data.experiment) <- NULL
  
  data.experiment$sessionNr <- as.numeric(factor(data.experiment$sessionNr))
  
  data.experiment$sessionTypeCode <- 0
  data.experiment$sessionTypeCode <- with(data.experiment, as.numeric(interaction(appCode, condCode, user_id)))
  data.experiment$SessionType <- with(data.experiment, interaction(App, Cond, user_id))
  
  save(data.experiment, VP.numbers, User.ids, file = "02_DataExperiment_labeledWithConds+SessionNrs.Rda")
  
  rm(list = ls())
}
  
if ( !file.exists("03_DataExperiment_labeledWithConds+SessionNrs+GameLogic.Rda") ) {
  
  load("02_DataExperiment_labeledWithConds+SessionNrs.Rda")
  
  #######################################################
  # EXTRACT GAME BASED FEATURES
  #######################################################
  
  # numbering Interactions and Tasks
  load.indices <- which(data.experiment$event == "loaded")
  load.indices <- load.indices - 1
  sessionNr.old <- 0
  task.Nr <- 0
  interaction.Nr <- 0
  loadCounter <- 1
  aimed.at.button <- FALSE
  hit.correct.button <- FALSE
  placed.correctly <- FALSE
  placed <- FALSE
  
  for(i in 1:dim(data.experiment)[1]){
    if (sessionNr.old != data.experiment$sessionNr[i]){
      interaction.Nr <- 0
      task.Nr <- 0
    }
  
    if(data.experiment$event[i] == "loaded"){
      interaction.Nr <- interaction.Nr + 1
      task.Nr <- task.Nr + 1
      loadCounter <- loadCounter + 1
      aimed.at.button <- FALSE
      hit.correct.button <- FALSE
      placed.correctly <- FALSE
      
    } else {
    
      if (data.experiment$App[i] == "Quiz"){
        if (data.experiment$event[i] %in% c("correct.button", "wrong.button")){
          if(hit.correct.button){
            task.Nr <- task.Nr + 1
          }
          hit.correct.button <- (data.experiment$event[i] == "correct.button")
          if (!aimed.at.button){
            aimed.at.button <- TRUE
          } else {
            interaction.Nr <- interaction.Nr + 1
          }
        }
      } else { # "Spell"
        if (data.experiment$event[i] %in% c("correct.button", "wrong.button")){
          if (!aimed.at.button){
            aimed.at.button <- TRUE
          } 
        }
        if (data.experiment$event[i] %in% c("correctly.placed", "wrong.placed")){
          # if (aimed.at.button){
          #   if (!placed){
              placed <- TRUE
              placed.correctly <- (data.experiment$event[i] == "correctly.placed")
          #   } else {
              # interaction.Nr <- interaction.Nr + 1
          #   }
          # }
        }
      }
      
      
    }
  
    sessionNr.old <- data.experiment$sessionNr[i]
    # print(c(i, interaction.Nr))
    data.experiment$interactionNr[i] <- interaction.Nr
    data.experiment$taskNr[i] <- task.Nr
    if (placed){
      interaction.Nr <- interaction.Nr + 1
      placed <- FALSE
    }
    if(placed.correctly){
      task.Nr <- task.Nr + 1
      placed.correctly <- FALSE
    }
    
    
  }
  
  # View(head(with(data.experiment[data.experiment$App == "Quiz",], data.frame(id, App, Cond, timestamp, event, sessionNr, interactionNr, taskNr, button_pressed, correct_answer, x_location, y_location)), n = 2000))
  # View(tail(with(data.experiment[data.experiment$App == "Quiz",], data.frame(id, App, Cond, freezing_duration, timestamp, event, sessionNr, interactionNr, taskNr, button_pressed, correct_answer, x_location, y_location)), n = 2000))
  # View(head(with(data.experiment[data.experiment$App == "Spell",], data.frame(id, App, Cond, timestamp, event, sessionNr, interactionNr, taskNr, button_pressed, correct_answer, x_location, y_location)), n = 2000))
  # View(tail(with(data.experiment[data.experiment$App == "Spell",], data.frame(id, App, Cond, freezing_duration, timestamp, event, sessionNr, interactionNr, taskNr, button_pressed, correct_answer, x_location, y_location)), n = 2000))
  
  
  data.experiment$SessionInteraction <- factor(with(data.experiment, interaction(sessionNr, interactionNr)))
  data.experiment$SessionTask <- factor(with(data.experiment, interaction(sessionNr, taskNr)))
  
  #save(data.experiment, file="SessionsDataStudie01.Rda")
  
  # dim(as.data.frame(table(data.experiment$SessionInteraction)))
  
  sessionMembers <- as.data.frame(table(data.experiment$SessionInteraction))
  dim(sessionMembers[sessionMembers$Freq < 2,]) # interactions with only one entry are artefacts
  
  data.experiment <- data.experiment[!(data.experiment$SessionInteraction %in% sessionMembers$Var1[sessionMembers$Freq < 2]),]
  rownames(data.experiment) <- NULL
  
  data.experiment$SessionInteraction <- factor(with(data.experiment, interaction(sessionNr, interactionNr)))
  data.experiment$SessionTask <- factor(with(data.experiment, interaction(sessionNr, taskNr)))
  
  dim(as.data.frame(table(data.experiment$SessionInteractionNr)))
  
  rownames(data.experiment) <- NULL
  
  # table(data.experiment$sessionNr)
  
  save(data.experiment, VP.numbers, User.ids, file = "03_DataExperiment_labeledWithConds+SessionNrs+GameLogic.Rda")
  
  rm(list = ls())
}

load("03_DataExperiment_labeledWithConds+SessionNrs+GameLogic.Rda")

pie(table(factor(with(data.experiment[data.experiment$event == "touch.down",], interaction(Cond, App)))), main=paste0("Frequency Distribution of Touch Down Events per Condition and App \n # Test Participants: ", length(User.ids)))
pie(table(factor(with(data.experiment[data.experiment$event == "touch.down" & data.experiment$user_id > 121,], interaction(Cond, App)))), main=paste0("Frequency Distribution of Touch Down Events per Condition and App whith working Quiz Freezing \n # Test Participants: ", length(User.ids[User.ids > 121])))

pie(table(factor(with(data.experiment, interaction(Cond, App)))), main=paste0("Frequency Distribution of Events per Condition and App \n # Test Participants: ", length(User.ids)))
pie(table(factor(with(data.experiment[data.experiment$user_id > 121,], interaction(Cond, App)))), main=paste0("Frequency Distribution of Events per Condition and App whith working Quiz Freezing \n # Test Participants: ", length(User.ids[User.ids > 121])))
# barchart(table(factor(with(data.experiment, interaction(Cond, App)))), main="Number of Events per Condition and App")
# barchart(table(factor(with(data.experiment[data.experiment$user_id > 121,], interaction(Cond, App)))), main="Number of Events per Condition and App whith working Quiz Freezing")


# table(data.experiment$sessionCode)
# table(data.experiment$Session)
# table(factor(with(data.experiment, interaction(Cond, App))))


```

# Extract General Touch Features

The events "touch.down" and "touch.release" are combined to "touch". The button-parameters of "touch.release" are renamed for "target.*".

```{r extract general touch features}

if ( !file.exists("04_part1_DataExperiment_generalTouchFeatures.Rda") ) {
  #######################################################
  # EXTRACTING GENERAL FEATURES
  #######################################################
  
  load("03_DataExperiment_labeledWithConds+SessionNrs+GameLogic.Rda")
  
  # extract touch duration, swipe length, swipe speed, time between touches
  tracking.touches.d <- subset(data.experiment, data.experiment$event=="touch.down")
  tracking.touches.u <- subset(data.experiment, data.experiment$event=="touch.release")
  
  ids.d <- tracking.touches.u$id-1
  ids.u <- tracking.touches.d$id+1
  
  touches.up <- tracking.touches.u[tracking.touches.u$id %in% ids.u,]
  touches.down <- tracking.touches.d[tracking.touches.d$id %in% ids.d,]
  
  touches.up$touch.duration <- touches.up$timestamp - touches.down$timestamp
  touches.down$touch.duration <- touches.up$timestamp - touches.down$timestamp
  
  touches.up$swipe_length <- sqrt((touches.down$x_location - touches.up$x_location)^2 + (touches.down$y_location - touches.up$y_location)^2)
  touches.up$swipe_length.x <- touches.up$x_location - touches.down$x_location
  touches.up$swipe_length.y <- touches.up$y_location - touches.down$y_location
  touches.up$swipe_speed <- touches.up$swipe_length / as.numeric(touches.up$touch.duration)
  touches.up$swipe_speed.x <- touches.up$swipe_length.x / as.numeric(touches.up$touch.duration)
  touches.up$swipe_speed.y <- touches.up$swipe_length.y / as.numeric(touches.up$touch.duration)
  # touches$isSwipe <- touches$swipe_length > 0
  # touches$missedTarget <- !touches$button_pressed
  touches.up$time_between_touches <- c(NA,touches.down$timestamp[2:nrow(touches.down)] - touches.up$timestamp[1:(nrow(touches.down)-1)])
  
  touches.up$target_height <- touches.up$button_height
  touches.up$target_origin_x <- touches.up$button_origin_x
  touches.up$target_origin_y <- touches.up$button_origin_y
  touches.up$target_touch_x_location <- touches.up$button_touch_x_location
  touches.up$target_touch_y_location <- touches.up$button_touch_y_location
  touches.up$target_width <- touches.up$button_width
  touches.up$x_location.release <- touches.up$x_location
  touches.up$y_location.release <- touches.up$y_location
  
  data.experiment$x_location.down <- data.experiment$x_location
  data.experiment$y_location.down <- data.experiment$y_location
  
  data.experiment$touch.duration[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$touch.duration
  data.experiment$swipe_length[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$swipe_length
  data.experiment$swipe_length.x[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$swipe_length.x
  data.experiment$swipe_length.y[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$swipe_length.y
  data.experiment$swipe_speed[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$swipe_speed
  data.experiment$swipe_speed.x[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$swipe_speed.x
  data.experiment$swipe_speed.y[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$swipe_speed.y
  data.experiment$time_between_touches[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$time_between_touches
  
  data.experiment$target_height[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$target_height
  data.experiment$target_origin_x[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$target_origin_x
  data.experiment$target_origin_y[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$target_origin_y
  data.experiment$target_touch_x_location[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$target_touch_x_location
  data.experiment$target_touch_y_location[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$target_touch_y_location
  data.experiment$target_width[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$target_width
  data.experiment$x_location.release[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$x_location.release
  data.experiment$y_location.release[data.experiment$event=="touch.down" & data.experiment$id %in% touches.down$id ] <- touches.up$y_location.release
  
  save(data.experiment, VP.numbers, User.ids, file = "04_part1_DataExperiment_generalTouchFeatures.Rda")
    
  rm(list = ls())
}

# ToDo: estimate differences to button centers

extractTouchAccuracy <- function(touches.experiment){
  
  apps <- attributes(touches.experiment$App)$levels
  conds <- attributes(touches.experiment$Cond)$levels
  users <- as.numeric(attributes(as.factor(touches.experiment$User))$levels)
  
  touches.experiment$button_center_x <- NA
  touches.experiment$button_center_y <- NA
  
  touches.experiment$difference.touch_buttonCenter_x <- NA
  touches.experiment$difference.touch_buttonCenter_y <- NA
  
  touches.experiment$touchAccuracy <- NA
  touches.experiment$touchAccuracy_x <- NA
  touches.experiment$touchAccuracy_y <- NA
  
  for(user in users){
    for(appName in apps){
      for(cond in conds){
        currentGameData <- touches.experiment[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release"),]
        l <- length(currentGameData$button_pressed)
        for(i in 1:l){
          touch_x <- currentGameData$x_location.down[i]
          touch_y <- currentGameData$y_location.down[i]
          
          if(currentGameData$button_pressed[i]){
            
            button_center_x <- currentGameData$button_origin_x[i] + currentGameData$button_width[i]/2
            button_center_y <- currentGameData$button_origin_y[i] + currentGameData$button_height[i]/2
            
          } else {
            
            j <- i
            
            while(!currentGameData$button_pressed[j] & (j<l)){
              j <- j+1
            }
            
            if (j > l){
              
              button_center_x <- NA
              button_center_y <- NA
              
            } else {
              
              button_center_x <- currentGameData$button_origin_x[j] + currentGameData$button_width[j]/2
              button_center_y <- currentGameData$button_origin_y[j] + currentGameData$button_height[j]/2
              
              currentGameData$button_width[i] <- currentGameData$button_width[j]
              currentGameData$button_height[i] <- currentGameData$button_height[j]
              
            }
          } # end check if button pressed
          
          currentGameData$button_center_x[i] <- button_center_x
          currentGameData$button_center_y[i] <- button_center_y
          
          currentGameData$difference.touch_buttonCenter_x[i] <- touch_x - button_center_x
          currentGameData$difference.touch_buttonCenter_y[i] <- touch_y - button_center_y
          
          currentGameData$touchAccuracy_x[i] <- (currentGameData$x_location[i]-currentGameData$button_center_x[i])/(0.5*currentGameData$button_width[i])
          currentGameData$touchAccuracy_y[i] <- (currentGameData$y_location[i]-currentGameData$button_center_y[i])/(0.5*currentGameData$button_height[i])
          currentGameData$touchAccuracy[i] <- currentGameData$touchAccuracy_x[i] * currentGameData$touchAccuracy_y[i]
          
          # print(with(currentGameData[i,], data.frame(button_pressed, correct_answer, x_location, button_origin_x, button_width, button_center_x, difference.touch_buttonCenter_x, y_location, button_origin_y, button_height, button_center_y, difference.touch_buttonCenter_y)))
        } # end for loop through data for one run
        
        touches.experiment$difference.touch_buttonCenter_x[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$difference.touch_buttonCenter_x
        touches.experiment$difference.touch_buttonCenter_y[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$difference.touch_buttonCenter_y
        
        touches.experiment$touchAccuracy_x[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$touchAccuracy_x
        touches.experiment$touchAccuracy_y[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$touchAccuracy_y
        touches.experiment$touchAccuracy[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$touchAccuracy
        
        # touches.experiment <- ddply(touches.experiment, c("User"), transform, touchAccuracy_x.std = scale(touchAccuracy_x))
        # touches.experiment <- ddply(touches.experiment, c("User"), transform, touchAccuracy_y.std = scale(touchAccuracy_y))
        # touches.experiment <- ddply(touches.experiment, c("User"), transform, touchAccuracy.std = scale(touchAccuracy))
        
        touches.experiment$button_center_x[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$button_center_x
        touches.experiment$button_center_y[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$button_center_y
        
        touches.experiment$button_width[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$button_width
        touches.experiment$button_height[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond & (touches.experiment$event == "touch.down" | touches.experiment$event == "touch.release")] <- currentGameData$button_height
        
        # View(head(with(touches.experiment[touches.experiment$User == user & touches.experiment$App == appName & touches.experiment$Cond == cond,], data.frame(button_pressed, correct_answer, x_location, button_origin_x, button_width, button_touch_x_location, button_center_x, difference.touch_buttonCenter_x, touchAccuracy_x, y_location, button_origin_y, button_height, button_touch_y_location, button_center_y, difference.touch_buttonCenter_y, touchAccuracy_y)) , 25))
      }
    }
  }
  
  # View(with(touches.experiment, data.frame(button_pressed, correct_answer, x_location, button_origin_x, button_width, button_center_x, difference.touch_buttonCenter_x, y_location, button_origin_y, button_height, button_center_y, difference.touch_buttonCenter_y)))
  
  
  return(touches.experiment)
}

if ( !file.exists("04_DataExperiment_generalTouchFeatures.Rda") ) {
  
  load("04_part1_DataExperiment_generalTouchFeatures.Rda")
  
  data.experiment <- extractTouchAccuracy(data.experiment)
  
  save(data.experiment, VP.numbers, User.ids, file = "04_DataExperiment_generalTouchFeatures.Rda")
    
  rm(list = ls())
}


```